Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2017-11-22 papers/cvpr2018/supplemental/classifier.tex
supplemental: cleaned up the writing

From the skeletons we generate locations in the center of potential merges. 
We extract a cubic region of interest around each location.
We experimented with three different region of interest side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our network.

@@

We experimented with several different network architectures before deciding on the one presented in our paper. 
We considered stochastic gradient descent with Nesterov momentum and the Adam optimizer.
In addition we toggled between a binary cross entropy and mean squared error loss function.
Also, we considered four varying input sizes that corresponding to different cube sizes output from the final max pooling layer. 
After running a brute force search over all of these possible architectures, we found that the best architecture used a SGD optimizer with Nesterov momentum, a mean squared error loss function, and an input size of $76 \times 76 \times 24$.

@@

Figure \ref{fig:architecture} shows the final architecture that produced the best results on the validation data. 
The input data was $76 \times 76 \times 24$ voxels in size with $3$ channels per voxel. 
This corresponds to an output size from the third layer of double convolution of $6 \times 6 \times 6$. 
This flattens to a vector of size $13,824$ which enters a dense layer of output size $512$ followed by another dense layer of output size $1$. 
All activation layers are Leaky ReLU with $\alpha=0.001$ except for the final layer which has a sigmoid activation layer.

>>>>

We generate locations for the potential merges from the skeletons using the algorithm in Section 3.2.
From these locations we extract a cubic region of interest.
We experimented with three different region of interest side lengths: $800 \textrm{nm}$, $1200 \textrm{nm}$, and $1600 \textrm{nm}$. 
Side lengths of $1600 \textrm{nm}$ performed better on the training and validation data on our networks.

@@

We experimented with several different network architectures before deciding on the one presented in our paper. 
We considered two optimizers: stochastic gradient descent with Nesterov momentum and Adam~\cite{kingma2014adam}.
In addition we tried two different loss functions: binary cross entropy and mean squared error.
We also experimented with four different input sizes that correspond to different cube sizes output from the final max pooling layer. 
After running a brute force search over all of these possible architectures, we found that the best architecture used a SGD optimizer with Nesterov momentum, a mean squared error loss function, and an input size of $76 \times 76 \times 24$.

@@

Figure \ref{fig:architecture} shows the final architecture that produced the best results on the validation data. 
The input data was $76 \times 76 \times 24$ voxels with $3$ channels per voxel. 
This corresponds to an output size from the third max pooling layer of $6 \times 6 \times 6$. 
This flattens to a $13,824$-element vector and two dense layers of output size $512$ and $1$ follow. 
All activation layers are Leaky ReLU with $\alpha=0.001$ except for the final layer which has a sigmoid activation.

### 2017-11-22 papers/cvpr2018/supplemental/performance.tex
supplemental: cleaned up the writing

All performance experiments ran on an Intel i7-6800K CPU 3.4 0GHz with a PASCAL Titan X GPU. 
All code is written in Python and will be freely available upon the paper decision.
We use the Keras deep learning library for our neural networks with Theano backend with cuDNN 7 acceleration for cuda 8.0.

@@

The network trained for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
The following tables show the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
In all instances the time for these three steps was less than 100 seconds.
Currently extracting the skeletons with the TEASER algorithm is the bottleneck to the process.
The skeleton for each segment takes around $20-30$ seconds to generate. 
However, the skeleton process is parallelizable and each segment can be processed independently.
Faster skeleton extraction is an important area for future research.

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{c c c } \hline
		& Kasthuri Vol. 1 & Kasthuri Vol. 2 \\ \hline
		Graph Generation & 34.76s & 35.90s \\
		Inference & 38.47s & 37.13s \\
		Multicut & 22.94s & 22.90s \\ \hline
		Total Time & 96.17s & 95.93s \\ \hline
	\end{tabular}
	\begin{tabular}{c c c } \hline
		& FlyEM Vol. 1 & FlyEM Vol. 2 \\ \hline
		Graph Generation & 46.52s & 48.97s \\
		Inference & 12.55s & 10.91s \\
		Multicut & 30.30s & 30.14s \\ \hline
		Total Time & 89.37s & 90.02s \\ \hline
	\end{tabular}
\end{table}

>>>>

All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. 
All code is written in Python and will be freely available upon the paper decision.
We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for cuda 8.0.

@@

The network trained for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
Table \ref{table:performance} shows the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
In all instances the time for these three steps combined was less than 100 seconds.
Currently extracting the skeletons with the TEASER algorithm is the bottleneck.
The skeleton for each label takes around $20-30$ seconds to generate. 
However, the process is parallelizable as each segment can be processed independently.
Faster skeleton extraction is an important area for future research, particularly to consider algorithms in different fields~\cite{fazekas2008skeletonization}.
There is some existing research of fast topologically preserving skeleton generation and their applications to existing medical images (e.g. blood vessels, the colon)~\cite{palagyi2001sequential}.

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{c c c } \hline
		& \textbf{Kasthuri Vol. 1} & \textbf{Kasthuri Vol. 2} \\ \hline
		Graph Generation & 34.76s & 35.90s \\
		Inference & 38.47s & 37.13s \\
		Multicut & 22.94s & 22.90s \\ \hline
		Total Time & 96.17s & 95.93s \\ \hline
		& \textbf{FlyEM Vol. 1} & \textbf{FlyEM Vol. 2} \\ \hline
		Graph Generation & 46.52s & 48.97s \\
		Inference & 12.55s & 10.91s \\
		Multicut & 30.30s & 30.14s \\ \hline
		Total Time & 89.37s & 90.02s \\ \hline
	\end{tabular}
	\caption{Performance of each step of the framework for all four datasets.}
	\label{table:performance}
\end{table}

### 2017-11-22 papers/cvpr2018/supplemental/skeletonization.tex
supplemental: cleaned up the writing

\section{Skeletonization}

more details regarding the skeletonization approach, which I believe was extra fast?

\subsection{Parameters}

\subsection{Performance Tests}

>>>>

\section{Graph Creation}

\subsection{Node Pruning}

We remove all nodes from the graph corresponding to labels with fewer than $t_{seg}$ voxels (Section 3.1).
Figure \ref{fig:node-pruning} shows the results of varying $t_{seg}$ on two different quantities for the Kasthuri training volume. 
The blue line indicates the number of nodes remaining in the graph.
The rate of node reduction decreases for larger thresholds since there are fewer labels of larger size. 
The green line shows the percent of voxels with a label pruned from the graph.
Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
These are locations which we cannot improve the variation of information scores.
This ``volume lost" grows at an increasing rate as the larger segments are removed. 
Based on these curves we set $t_{seg} = 20000$ voxels.
With this threshold, we prune over half of the labels that correspond to around $1.5\%$ of the total volume.

\subsection{Edge Pruning}

There are two parameters in the two-pass edge pruning algorithm, $t_{low}$ and $t_{high}$ (Section 3.2). 
The resulting graph should have the highest possible percentage of split errors still present while keeping the number of total edges low. 
We perform a search over varying thresholds for $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of true splits that keeps the number of total edges less than $6 \times$ the number of split errors.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.95\linewidth]{./figures/node-threshold.png}
		\caption{The number of remaining nodes after increasing the threshold (blue) and the number of voxels with this label as a percent of the total volume (green). }
		\label{fig:node-pruning}
	\end{center}
\end{figure}
